\chapter{chapter 1}
\label{ch:chapter1}

I used the commercial Latex editor Texpad (1.8.9), because I needed to speed up the initial setup time.  To focus on the content and structure I first wrote a short draft with Markup. I was quite in a hurry when I found out, that Markup to Latex conversion is not that gapless as I hoped.

When everything went well you should see the following content:

\begin{itemize}
	\item Title page
	\item \textit{Blank Page}
	\item Acknowledgements
	\item \textit{Blank Page}
	\item Abstract
	\item \textit{Blank Page}
	\item Table of contents
	\item \textit{Blank Page}
	\item List of Abbreviations (nomenclature)
	\item \textit{Blank Page}
	\item List of Figures
	\item \textit{Blank Page}
	\item List of Tables
	\item \textit{Blank Page}
	\item List of source codes (listings)
	\item \textit{Blank Page}
	\item Chapter1
	\item Chapter2
	\item \textit{Blank Page}
	\item Chapter3
	\item References (Bibliography)
	\item Declaration
\end{itemize}

Internal links to other pages of the document should be green, external links (URLs) should appear blue. If you set the option media=print, these colors will be changed to black. You find this line in \textit{thesis.tex}.

To have source code linted (colored depending on input e.g. variables other than functions), have a look at the "minted" package on CTAN \href{http://tug.ctan.org/tex-archive/macros/latex/contrib/minted/minted.pdf}{here}.

\begin{verbatim}
\documentclass[media=screen]{SPhdThesis}
\end{verbatim}

You can speed up rendering by using only placeholders instead of images by adding the "draft" option:

\begin{verbatim}
\documentclass[media=screen, draft]{SPhdThesis}
\end{verbatim}



If you decide to get rid of an unnecessary part of the frontmatter, just comment it out in the main \.tex file: \(thesis.tex\). 

\begin{listing}
\begin{verbatim}
	\begin{frontmatter}
		\input{acknowledgments} %
		\SgIntClearDoublePage
		\input{quotation} %
		\input{abstract} %
		\SgAddToc %  Table of contents.
		\SgAddAbbrv % List of abbreviations
		\SgAddLof %  List of figures.
		\SgAddLot %  List of tables.
		\SgAddLos %  List of source codes
		\SgAddLoa %  List of algorithms.
	\end{frontmatter}
\end{verbatim}
\caption{Latex code in the main document \textit{thesis.tex}}
\label{lst:latexexample}
\end{listing}

\section{citation examples}
\label{sec:citeationexamples}

The exact styling used by the citation commands derives from the chosen .bst (bibtex style document).

Always think of proper citation - this is Author year style as defined in the .bst

\begin{verbatim}
	\cite{cooper_about_2014}
\end{verbatim}
Example:	
	\cite{cooper_about_2014}

But you can also only cite the year of a publication 

\begin{verbatim}
	\citeyear{cooper_about_2014}
\end{verbatim} 

Example:
	\citeyear{cooper_about_2014}

There is even a command to put the year in parenthesis 


\begin{verbatim}
	\citeyearpar{cooper_about_2014}.
\end{verbatim} 

Example:
\citeyearpar{cooper_about_2014}

To include a reference in the bibliography without having to cite it in the text, use:

\begin{verbatim}
	\nocite{cooper_about_2014}
\end{verbatim}

	or to include all entries inside the .bib file, even the not cited ones:

\begin{verbatim}
	\nocite*	
\end{verbatim}
\nocite*

% nomenclature example, for List of Abbreviations

Don't forget to feed your nomenclature:
Communication is the key to superior results, think of
computer interface (HCI\nomenclature{HCI}{Human Computer Interface}) aspects.


\section{Motivation}
\label{sec:ch01_motivation}

Always think of people you enjoy.
% 

\input{fig_barbara}

\pagebreak

\section{Structure}
\label{subsec:ch01_structure}

In chapter \ref{ch:chapter2} you find a link back to this chapter.

